Regular singular Volterra equations on complex domains

### 2024-09-19 sima/reg-sing-volterra_sima.tex
change notation for convolution, dropping the "prime" and "double prime" notation
Format for print

\documentclass[review]{siamart220329}

@@

% list formatting
\newlist{conditions}{itemize}{1}
\setlist[conditions]{leftmargin=26mm, rightmargin=12mm}
\makeatletter
% hat tip TeX.SE user31729
%   https://tex.stackexchange.com/a/328393/6934
\newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
\newcommand{\condconst}[2]{\item[($\text{\textsc{#1}} \mid #2$)]\protected@edef\@currentlabel{$\text{\textsc{#1}} \mid #2$}}
\makeatother

@@

% revision highlighting
\newif\ifhighlightrevs
\highlightrevstrue
\ifhighlightrevs
\newenvironment{revtwo}{\color{revred}}{\color{black}}
\newcommand{\revtwotext}[1]{\textcolor{revred}{#1}}
\else
\newenvironment{revtwo}{}{}
\newcommand{\revtwotext}[1]{#1}
\fi

% notation change highlighting
\newif\ifhighlightnewnotation
\highlightnewnotationtrue
\ifhighlightnewnotation
\newenvironment{newnot}{\color{orange}}{\color{black}}
\newcommand{\newnottext}[1]{\textcolor{orange}{#1}}
\newenvironment{oldnot}{\color{cyan}}{\color{black}}
\newcommand{\oldnottext}[1]{\textcolor{cyan}{#1}}
\else
\newenvironment{newnot}{}{}
\newenvironment{oldnot}{}{}
\newcommand{\newnottext}[1]{#1}
\fi

@@

Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$, and satisfies the following condition.
\begin{conditions}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ does not contain $\zeta = 0$, we will always omit that starting point from the path.
\end{conditions}
For the applications we have in mind, $\domain$ typically resembles the set pictured below.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[ietcoast!33, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[ietcoast!33!black] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we will be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel $\hardker$ and a regular singularity at $\zeta = 0$.

@@

To see that the fixed point is unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$. Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion. Next, observe that for any $\Lambda'' \ge \Lambda$, the map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda''}(\Omega)$. The inclusion $\singexp{\rho-1}{\Lambda}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda''}(\Omega)$ must send the unique fixed point in the smaller space to the unique fixed point in the larger one. Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
\end{proof}
\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}. The base point for the construction can be chosen arbitrarily. Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} ensures that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$. Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\domain)$ that makes $\solwhole = \solproto + \solptb$ a solution of 
\begin{equation}\label{eqn:orig-homog}
\solwhole = \volterra \solwhole.
\end{equation}
Observing that
\begin{align*}
\volterra \solproto & = \hardpart\solproto + \softpart\solproto \\
& = \solproto + \softpart \solproto,
\end{align*}
we rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
\begin{align}
\solproto + \solptb & = \volterra\solproto + \volterra\solptb \nonumber \\
& = \solproto + \softpart\solproto + \volterra\solptb \nonumber \\
\solptb & = \softpart\solproto + \volterra\solptb. \label{eqn:equiv-inhomog}
\end{align}
Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$. Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$. Equivalently, equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
\end{proof}
\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
First, suppose $\rho \in (\tau, \tau+\gamma)$. In this case, the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$. Lemma~\ref{lem:perturbed_volterra} then guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.

@@

Since $P$ is a monic polynomial whose roots are all simple, $1/P(-\zeta)$ has the nice partial fraction decomposition
\[ \frac{1}{P(-\zeta)} = \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
where $\roots$ is the zero set of $P$ \cite[Section 1.4, Exercise~2]{ahlfors}. 
It follows that
\begin{align*}
-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} & = \sum_{-\beta \in \roots} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} \\
& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q\big(-\zeta(a')\big)}{P'(-\alpha)\,(\zeta(a) - \alpha)}.
\end{align*}
Now we expand $Q$ around $-\alpha$, using the decomposition $Q(-\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(-\zeta)$ to split up the last term of the expression above:
\begin{equation}\label{eqn:split-numerator}
-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.
\end{equation}
First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. It follows from equation~\eqref{eqn:split-numerator} that
\begin{align*}
-\frac{Q(-\zeta)}{P(-\zeta)} & =
\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(-\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}\,.
\end{align*}
Recalling that $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, we conclude that
\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)}\,. \]
Since $Q$ and $Q_\alpha$ are polynomials, the right-hand side is bounded on any neighborhood of $\zeta = \alpha$ that avoids the other roots of $p$ and avoids infinity.

Next, we want to show that for any $\sigma > \tau_\alpha$, the bound
\[ |\zeta(a) - \alpha| \left|\frac{q(a')}{p(a)}\right| < \sigma \]
holds when $a$ and $a'$ are close enough to $\zeta = \alpha$. Taking the absolute value of both sides of equation~\eqref{eqn:split-numerator}, and using the assumption that $\tau_\alpha$ is real and positive, we see that
\begin{align*}
\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha\,.
\end{align*}
By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
\[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
arbitrarily small. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
\[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
arbitrarily small. Hence, for any $\sigma > \tau_\alpha$, the bound
\[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$.
\begin{verify}
\par Solution of Ahlfors exercise. First, observe that
\begin{align*}
P(t) &= (t + \beta_1) \cdots (t + \beta_d) \\
P'(t) &= \sum_k \left[ \prod_{j \neq k} (t + \beta_j) \right] \\
P'(-\beta_1) &= \prod_{j\neq 1} (-\beta_1 + \beta_j) 
\end{align*}
Then we see that
\begin{align*}
\frac{1}{P(t)} & = \sum_{j} \frac{\pi_j}{t + \beta_j}\\
-\frac{P'(t)}{P(t)^2} &= -\sum_{j} \frac{\pi_\beta}{(t + \beta_j)^2}\\
P'(t) &= \sum_{j} \pi_j \left(\frac{P(t)}{t + \beta_j}\right)^2\\
P'(-\beta_1) &=  \pi_1 \prod_{j\neq 1} (-\beta_1+\beta_j)^2\\
\frac{1}{P'(-\beta_1)} &= \pi_1
\end{align*}
\end{verify}
\item Condition~\eqref{cond:diag-basic} {\em on $\hardpart^\alpha$ is satisfied.}

>>>>

\documentclass[final]{siamart220329}

@@

% list formatting
\setlist[itemize]{topsep=3mm, itemsep=1.8mm, parsep=1.2mm}
\newlist{conditions}{itemize}{1}
\setlist[conditions]{leftmargin=26mm, rightmargin=12mm, topsep=2.5mm, itemsep=1.8mm, parsep=1.2mm}
\makeatletter
% hat tip TeX.SE user31729
%   https://tex.stackexchange.com/a/328393/6934
\newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
\newcommand{\condconst}[2]{\item[($\text{\textsc{#1}} \mid #2$)]\protected@edef\@currentlabel{$\text{\textsc{#1}} \mid #2$}}
\makeatother

@@

% revision highlighting
\newif\ifhighlightrevs
\highlightrevsfalse
\ifhighlightrevs
\newenvironment{revtwo}{\color{revred}}{\color{black}}
\newcommand{\revtwotext}[1]{\textcolor{revred}{#1}}
\else
\newenvironment{revtwo}{}{}
\newcommand{\revtwotext}[1]{#1}
\fi

% notation change highlighting
%%\newif\ifhighlightnewnotation
%%\highlightnewnotationfalse
%%\ifhighlightnewnotation
%%\newenvironment{newnot}{\color{orange}}{\color{black}}
%%\newcommand{\newnottext}[1]{\textcolor{orange}{#1}}
%%\newenvironment{oldnot}{\color{cyan}}{\color{black}}
%%\newcommand{\oldnottext}[1]{\textcolor{cyan}{#1}}
%%\else
%%\newenvironment{newnot}{}{}
%%\newenvironment{oldnot}{}{}
%%\newcommand{\newnottext}[1]{#1}
%%\fi

@@

Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$, and satisfies the following condition.
\begin{conditions}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ does not contain $\zeta = 0$, we will always omit that starting point from the path.
\end{conditions}
For the applications we have in mind, $\domain$ typically resembles the set pictured below.
\vspace{2mm}

\begin{center}
\begin{tikzpicture}[scale=0.92]
\newcommand{\spill}{4}
\fill[ietcoast!33, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[ietcoast!33!black] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we will be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel $\hardker$ and a regular singularity at $\zeta = 0$.

@@

To see that the fixed point is unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$. Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion. Next, observe that for any $\Lambda'' \ge \Lambda$, the map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda''}(\Omega)$. The inclusion $\singexp{\rho-1}{\Lambda}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda''}(\Omega)$ must send the unique fixed point in the smaller space to the unique fixed point in the larger one. Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
\end{proof}
\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}. The base point for the construction can be chosen arbitrarily. Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} ensures that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$. Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\domain)$ that makes $\solwhole = \solproto + \solptb$ a solution of 
\begin{equation}\label{eqn:orig-homog}
\solwhole = \volterra \solwhole.
\end{equation}
Observing that
\begin{align*}
\volterra \solproto & = \hardpart\solproto + \softpart\solproto \\
& = \solproto + \softpart \solproto,
\end{align*}
we rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
\begin{align}
\solproto + \solptb & = \volterra\solproto + \volterra\solptb \nonumber \\
& = \solproto + \softpart\solproto + \volterra\solptb \nonumber \\
\solptb & = \softpart\solproto + \volterra\solptb. \label{eqn:equiv-inhomog}
\end{align}
Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$. Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$. Equivalently, equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
\end{proof}
\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
First, suppose $\rho \in (\tau, \tau+\gamma)$. In this case, the inclusion
\[\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)\]
given by Proposition~\ref{prop:inclus-lt-pow-alg} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$. Lemma~\ref{lem:perturbed_volterra} then guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.

@@

Since $P$ is a monic polynomial whose roots are all simple, $1/P(-\zeta)$ has the nice partial fraction decomposition
\[ \frac{1}{P(-\zeta)} = \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
where $\roots$ is the zero set of $P$ \cite[Section 1.4, Exercise~2]{ahlfors}. 
It follows that
\begin{align*}
-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} & = \sum_{-\beta \in \roots} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} \\
& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q\big(-\zeta(a')\big)}{P'(-\alpha)\,(\zeta(a) - \alpha)}.
\end{align*}
Now we expand $Q$ around $-\alpha$, using the decomposition
\[ Q(-\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(-\zeta) \]
to split up the last term of the expression above:
\begin{multline}\label{eqn:split-numerator}
-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \\
\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.    
\end{multline}
First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. It follows from equation~\eqref{eqn:split-numerator} that
\begin{align*}
-\frac{Q(-\zeta)}{P(-\zeta)} & =
\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(-\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}\,.
\end{align*}
Recalling that $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, we conclude that
\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)}\,. \]
Since $Q$ and $Q_\alpha$ are polynomials, the right-hand side is bounded on any neighborhood of $\zeta = \alpha$ that avoids the other roots of $p$ and avoids infinity.

Next, we want to show that for any $\sigma > \tau_\alpha$, the bound
\[ |\zeta(a) - \alpha| \left|\frac{q(a')}{p(a)}\right| < \sigma \]
holds when $a$ and $a'$ are close enough to $\zeta = \alpha$. Taking the absolute value of both sides of equation~\eqref{eqn:split-numerator}, and using the assumption that $\tau_\alpha$ is real and positive, we see that
\begin{align*}
\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \\ & \hspace{-15mm} \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \\
& \hspace{-15mm} \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha\,.
\end{align*}
By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
\[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
arbitrarily small. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
\[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
arbitrarily small. Hence, for any $\sigma > \tau_\alpha$, the bound
\[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$.
\begin{verify}
\par Solution of Ahlfors exercise. First, observe that
\begin{align*}
P(t) &= (t + \beta_1) \cdots (t + \beta_d) \\
P'(t) &= \sum_k \left[ \prod_{j \neq k} (t + \beta_j) \right] \\
P'(-\beta_1) &= \prod_{j\neq 1} (-\beta_1 + \beta_j) 
\end{align*}
Then we see that
\begin{align*}
\frac{1}{P(t)} & = \sum_{j} \frac{\pi_j}{t + \beta_j}\\
-\frac{P'(t)}{P(t)^2} &= -\sum_{j} \frac{\pi_\beta}{(t + \beta_j)^2}\\
P'(t) &= \sum_{j} \pi_j \left(\frac{P(t)}{t + \beta_j}\right)^2\\
P'(-\beta_1) &=  \pi_1 \prod_{j\neq 1} (-\beta_1+\beta_j)^2\\
\frac{1}{P'(-\beta_1)} &= \pi_1
\end{align*}
\end{verify}
\item Condition~\eqref{cond:diag-basic} {\em on $\hardpart^\alpha$ is satisfied.}
